quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-05 paper-quollr.Rmd
Updated the layouts

error_limb_umap <- read_rds("data/limb_muscles/error_limb_muscles_umap_n-neigbors_30_min-dist_0.1.rds")
error_limb_tsne <- read_rds("data/limb_muscles/error_limb_muscles_tsne_perplexity_30.rds")
error_limb_phate <- read_rds("data/limb_muscles/error_limb_muscles_phate_knn_5.rds")
error_limb_trimap <- read_rds("data/limb_muscles/error_limb_muscles_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")
error_limb_pacmap <- read_rds("data/limb_muscles/error_limb_muscles_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

@@

error_limb <- error_limb |>
  mutate(method = factor(method,
                         levels = c("UMAP_30_min_dist_0.1","tsne_30", "phate_5", "trimap_n-inliers_12_n-outliers_4_n-random_3", "pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2")))
```

>>>>

error_limb_umap <- read_rds("data/limb_muscles/error_limb_muscles_umap_n-neigbors_15_min-dist_0.1.rds")
error_limb_tsne <- read_rds("data/limb_muscles/error_limb_muscles_tsne_perplexity_30.rds")
error_limb_phate <- read_rds("data/limb_muscles/error_limb_muscles_phate_knn_5.rds")
error_limb_trimap <- read_rds("data/limb_muscles/error_limb_muscles_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")
error_limb_pacmap <- read_rds("data/limb_muscles/error_limb_muscles_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

@@

error_limb <- error_limb |>
  mutate(method = factor(method,
                         levels = c("UMAP_15_min_dist_0.1","tsne_30", "phate_5", "trimap_n-inliers_12_n-outliers_4_n-random_3", "pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2")))
```
